Excerno analysis

### 2022-08-18 paper_analysis.Rmd
Updated analysis with 6 real samples

```{r}
for (i in 1:length(vcf_files)) {
  name <- vcf_files[i]
  vcf <- read.vcfR(name)
  filter_name <- str_replace_all(name,"vcf","high.vcf.gz")

  gq <-  extract.gt(vcf, element="GQ", as.numeric=TRUE)
  write.vcf(vcf[which(gq[,1]>30),], file=filter_name)
  gunzip(filter_name)
}
```

@@

vcf_files <- list.files(path="supplied_results",pattern = "high.vcf", full.names = TRUE)
excerno_vcf(vcf_files,method="nmf",2)
```

@@

  # Calculate sensitivity and speficifty
  (sens <-  tp /all_true)
  (spec <- tn /all_false)
  (ffpe_pct <- all_false/(all_false+all_true))
  (total <- all_false+all_true)

  tibble(name=sample_name, sens=sens, spec=spec, 
         ffpe.pct = ffpe_pct*100, total=total)
}
```

@@

```{r}
vcf_files <- list.files(pattern = "vcf", full.names = TRUE)
sample_names = c("MLHG10_10", "MSH6_1","MSH6_2", "MSH6_8", "PMS2_10", "PMS2_09")
```

And we generate the table with informaton from the samples

```{r}
1:6 %>%
  map_dfr(~get_metrics(vcf_files[.x], sample_names[.x])) %>%
  arrange(desc(ffpe.pct)) %>%
  mutate_if(is.numeric, format, digits=1)%>%
  kbl() %>%
  kable_styling()

>>>>

```{r eval=FALSE}
for (i in 1:length(vcf_files)) {
  name <- vcf_files[i]
  vcf <- read.vcfR(name)
  filter_name <- str_replace_all(name,"vcf","dna.vcf.gz")
  out_vcf_name <- str_replace_all(name,"vcf", "dna.vcf")

  gq <-  extract.gt(vcf, element="GQ", as.numeric=TRUE)
  write.vcf(vcf[which(gq[,1]>30),], file=filter_name)
  gunzip(filter_name, out_vcf_name)
}
```

@@

vcf_files <- list.files(path="supplied_results",pattern = "dna.vcf", full.names = TRUE)
excerno_vcf(vcf_files,method="nmf",2)
```

@@

  # Calculate sensitivity and speficifty
  (sens <-  tp /all_true)
  (spec <- tn /all_false)
  (ffpe_pct <- all_false/(all_false+all_true))
  (total <- all_false+all_true)
  accuracy <- (tp + tn)/(all_true+all_false)

  tibble(Name=sample_name, `% FFPE`= round(ffpe_pct*100), `# Mutations`=total,
         Accuracy=accuracy, Specificity=spec, Sensitivity=sens)
}
```

@@

```{r}
vcf_files <- list.files(pattern = "vcf", full.names = TRUE)
sample_names = c("MLH1G_10", "MSH6_1","MSH6_2", "MSH6_8", "PMS2_10", "PMS2_9")
```

And we generate the table with information from the samples

```{r}
(perf_tbl <- 1:6 %>%
  map_dfr(~get_metrics(vcf_files[.x], sample_names[.x])) %>%
  arrange(desc(`% FFPE`)) %>%
  mutate(`% FFPE`=str_c(`% FFPE`,"%")) %>%
  mutate(across(c("Accuracy","Sensitivity", "Specificity"),
                ~format(.x,digits=2, justify="right")))%>%
  mutate(across(c(`# Mutations`), ~format(.x,big.mark=",", justify="right"))) %>%
  kbl(caption = "Table 1. Assessment of excerno on real samples", 
      align=c("l", rep("r",5))) %>%
  kable_classic(full_width = F, html_font = "Cambria"))

#save_kable(perf_tbl,"paper_figures/table_1.pdf")
